My title

### 2023-03-21 outputs/paper/paper.qmd
small changes in the codes for plot

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Ruibo Sun
thanks: "https://github.com/ruibosun/how-parents-affect-childrens-education"
date: "`r Sys.time()`"
date-format: "12-03-2023"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
#bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false
library(broom)
library(knitr)
library(kableExtra)
library(tidyverse)
library(dplyr)
library(here)
library(haven)
library(scales)
library(dplyr)
library(purrr)
library(forcats)
```

@@

# Get the summary statistics and tidy them up
tidy_summary <- tidy(summary(model))

# Create a data frame for the tidy summary
summary_df <- as.data.frame(tidy_summary)

# # Rename the row names
# row_names <- c("Intercept", "Mother's Prestiges Score", "Father's Prestiges Score", "Father's Education", "Mother's Education")
# rownames(summary_df) <- row_names

# Rename the column names
col_names <- c("Term", "Estimate", "Std. Error", "t value", "Pr(>|t|)")
colnames(summary_df) <- col_names

# Print the summary table with kableExtra
library(kableExtra)
kable(summary_df, align = c("l", "r", "r", "r", "r"),
      caption = "Summary of Linear Regression Model")
```
```{r}
#| message: false
#| echo: false
#| warning: false
#| label: tbl-degree
#| tbl-cap: Respondents' Degree in 2021 Survey

@@

  # geom_histogram(bins = 15, fill = "lightblue", color = "white") +
  labs(title = "Histogram of Respondents' Education", x = "Education (in Years)", y = "Desensity") +
   scale_x_continuous(breaks = seq(0, 20, by = 1))+
  theme_bw()
```

@@

tb0%>%kable()
```

@@

##edit this
ggplot(cleaned_data, aes(x = mapres10)) +
  geom_histogram(aes(y = ..density.., fill = "Mother's Prestige Score"), alpha = 1, binwidth = 1, color = "black")+
  geom_histogram(aes(x = papres10, y = ..density.., fill = "Father's Prestige Score"), alpha = 0.8, binwidth = 1, color = "black") +
  scale_fill_manual(values = c("Mother's Prestige Score" = "darkgreen", "Father's Prestige Score" = "lightgreen"), name = "Variables") +
  labs(title = "Mother's and Father's Prestige Score",
       x = "Prestige Score",
       y = "Density") +
  theme_bw()
```

@@

```{r}
#| label: fig-birth
#| fig-cap: Birthplace of the Respondent \n (if outside of US)
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 4

ggplot(cleaned_data, aes(x = educ, fill = factor(born))) +
  geom_histogram(position = "dodge", binwidth = 1.5, alpha = 0.5, color = "black")+
   labs(title = "Education and Birthplace (if outside of US) for the Respondent",
       x = "Education (in Years)",
       y = "Count",
       fill = "Birthplace of the Respondent \n (if outside of US)")+
  theme_bw()
```

```{r}
#| label: fig-region
#| fig-cap: Respondent's Living Region at Age of 16 v.s. Education
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 4
ggplot(cleaned_data, aes(x = educ,fill = factor(reg16))) +
  geom_histogram(binwidth = 2, color = "black") +
  facet_wrap(~ reg16, ncol = 3)+
  labs(title = "Respondent's Living Region at Age of 16 v.s. Education",
       x = "Education (in Years)",
       y = "Count")+
  theme_bw()+
  theme(legend.position = "none")
```

```{r}
#| label: fig-maincome
#| fig-cap: Education vs Mother's Education with respect to Family Income
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 4
ggplot(cleaned_data, aes(x = educ, y = maeduc, color = incom16)) +
  geom_jitter() +
  stat_smooth(method = "lm", se = FALSE) +
  facet_wrap(~incom16)+
  labs(title = "Education vs Mother's Education with respect to Family Income",
       x = "Education (in Years)",
       y = "Mother's Educaion (in Years)",
       color = "Family Income \n (at Age of 16)") +
  scale_color_discrete(name = "Family Income \n (at Age of 16)") +
  theme_bw()
```

```{r}
#| label: fig-paincome
#| fig-cap: Education vs Father's Education with respect to Family Income
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 4
ggplot(cleaned_data, aes(x = educ, y = paeduc, color = incom16)) +
  geom_jitter() +
  stat_smooth(method = "lm", se = FALSE) +
  facet_wrap(~incom16)+
  labs(title = "Education vs Father's Education with respect to Family Income",
       x = "Education (in Years)",
       y = "Father's Educaion (in Years)",
  color = "Family Income \n (at Age of 16)") +
  scale_color_discrete(name = "Family Income \n (at Age of 16)") +
  theme_bw()
```

@@

## Weaknesses and next steps {#sec-weaknesses}
*problems with prestige score:*
Subjectivity: Even measures of prestige that attempt to capture objective indicators of social status, such as income or educational attainment, are still subject to subjective interpretation. People's perceptions of what constitutes a high-prestige occupation may vary based on their own cultural, social, or personal biases.

@@

*problems with missing data:*
Reduced statistical power is one such issue, which lowers the likelihood of rejecting the null hypothesis when it is false.
Missing data can also cause bias in parameter estimation.
The representativeness of the sample can also be reduced due to missing data.
The analysis of the study can become more complex when missing data is present.
These problems can threaten the validity of the trials and lead to invalid conclusions.
(https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3668100/)

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Ruibo Sun
thanks: "https://github.com/ruibosun/how-parents-affect-childrens-education"
date: "`r Sys.time()`"
date-format: "12-03-2023"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false
library(broom)
library(knitr)
library(kableExtra)
library(tidyverse)
library(dplyr)
library(here)
library(haven)
library(scales)
library(dplyr)
library(purrr)
library(forcats)
library(patchwork)
```

@@

modelsummary::modelsummary(
  list(
    "Children's Education" = model
  ),
  fmt = 2,
  statistic = "conf.int"
)
# 
# # Get the summary statistics and tidy them up
# tidy_summary <- tidy(summary(model))
# 
# # Create a data frame for the tidy summary
# summary_df <- as.data.frame(tidy_summary)
# 
# # # Rename the row names
# # row_names <- c("Intercept", "Mother's Prestiges Score", "Father's Prestiges Score", "Father's Education", "Mother's Education")
# # rownames(summary_df) <- row_names
# 
# # Rename the column names
# col_names <- c("Term", "Estimate", "Std. Error", "t value", "Pr(>|t|)")
# colnames(summary_df) <- col_names
# 
# # Print the summary table with kableExtra
# 
# kable(summary_df, align = c("l", "r", "r", "r", "r"),
#       caption = "Summary of Linear Regression Model")
```

```{r}
#| message: false
#| echo: false
#| warning: false
#| label: tbl-degree
#| tbl-cap: Respondents' Degree in 2021 Survey

@@

  # geom_histogram(bins = 15, fill = "lightblue", color = "white") +
  labs(title = "Histogram of Respondents' Education", x = "Education (in Years)", y = "Desensity") +
  scale_x_continuous(breaks = seq(0, 20, by = 1)) +
  theme_bw()
```

@@

tb0 %>% kable()
```

@@

#prestige score distribution
ggplot(cleaned_data, aes(x = mapres10)) +
  geom_histogram(aes(y = ..density.., fill = "Mother's Prestige Score"), alpha = 1, binwidth = 1, color = "black")+
  geom_histogram(aes(x = papres10, y = ..density.., fill = "Father's Prestige Score"), alpha = 0.8, binwidth = 1, color = "black") +
  scale_fill_manual(values = c("Mother's Prestige Score" = "darkgreen", "Father's Prestige Score" = "lightgreen"), name = "Variables") +
  labs(title = "Mother's and Father's Prestige Score",
       x = "Prestige Score",
       y = "Density") +
  theme_bw()
```

```{r}
#| label: fig-presandeduc
#| fig-cap: Mother's and Father's Prestige Score
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 4
#pres vs. educ
p1 <- ggplot(cleaned_data, aes(x=educ, y=papres10)) +
  geom_point(color="#69b3a2", size=2) +
  ggtitle("Father's Prestige Score vs Children's Education") +
  labs(x="Education (in Years)", y="Father's Prestige Score")+
  theme_bw()
p2 <- ggplot(cleaned_data, aes(x=educ, y=mapres10)) +
  geom_point(color="darkgreen",size=2) +
  ggtitle("Mother's Prestige Score vs Children's Education") +
  labs(x="Education (in Years)", y="Mother's Prestige Score")+
  theme_bw()

p1 + p2
```

@@

```{r}
#| label: fig-birth
#| fig-cap: Birthplace of the Respondent (if outside of US)
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 4

ggplot(cleaned_data, aes(x = educ, fill = factor(born))) +
  geom_histogram(position = "dodge", binwidth = 1.5, alpha = 0.5, color = "black")+
   labs(title = "Education and Birthplace (if outside of US) for the Respondent",
       x = "Education (in Years)",
       y = "Count",
       fill = "Birthplace of the Respondent (if outside of US)")+
  theme_bw()
```

```{r}
#| label: fig-region
#| fig-cap: Respondent's Living Region at Age of 16 v.s. Education
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 4
ggplot(cleaned_data, aes(x = educ,fill = factor(reg16))) +
  geom_histogram(binwidth = 2, color = "black") +
  facet_wrap(~ reg16, ncol = 2)+
  labs(title = "Respondent's Living Region at Age of 16 v.s. Education",
       x = "Education (in Years)",
       y = "Count")+
  theme_bw()+
  theme(legend.position = "none")
```

```{r}
#| label: fig-maincome
#| fig-cap: Education vs Mother's Education with respect to Family Income
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 4
ggplot(cleaned_data, aes(x = educ, y = maeduc, color = incom16)) +
  geom_jitter() +
  stat_smooth(method = "lm", se = FALSE) +
  facet_wrap(~incom16)+
  labs(title = "Education vs Mother's Education with respect to Family Income",
       x = "Education (in Years)",
       y = "Mother's Educaion (in Years)",
       color = "Family Income (at Age of 16)") +
  scale_color_discrete(name = "Family Income (at Age of 16)") +
  theme_bw()
```

```{r}
#| label: fig-paincome
#| fig-cap: Education vs Father's Education with respect to Family Income
#| echo: false
#| warning: false
#| message: false
#| fig-width: 8
#| fig-height: 4

ggplot(cleaned_data, aes(x = educ, y = paeduc, color = incom16)) +
  geom_jitter() +
  stat_smooth(method = "lm", se = FALSE) +
  facet_wrap(~incom16)+
  labs(title = "Education vs Father's Education with respect to Family Income",
       x = "Education (in Years)",
       y = "Father's Educaion (in Years)",
  color = "Family Income (at Age of 16)") +
  scale_color_discrete(name = "Family Income (at Age of 16)") +
  theme_bw()
```

@@

## Weaknesses and next steps {#sec-weaknesses}
*problems with prestige score:*

Subjectivity: Even measures of prestige that attempt to capture objective indicators of social status, such as income or educational attainment, are still subject to subjective interpretation. People's perceptions of what constitutes a high-prestige occupation may vary based on their own cultural, social, or personal biases.

@@

*problems with missing data:*

Reduced statistical power is one such issue, which lowers the likelihood of rejecting the null hypothesis when it is false.
Missing data can also cause bias in parameter estimation.
The representativeness of the sample can also be reduced due to missing data.
The analysis of the study can become more complex when missing data is present.
These problems can threaten the validity of the trials and lead to invalid conclusions.
(https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3668100/)
